%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}

\def\jobtitle{Holistic Technologist}

\def\firstname{Steffen}
\def\middlename{Lars}
\def\initial{L.}
\def\lastname{Norgren}
\def\address{\href{https://goo.gl/maps/z8Kai5RWiDqzTpoi7}{1440 East Broadway,
Vancouver, BC
Canada V5N c5P2}}
\def\email{\href{mailto:steffen@norgren.ca}{steffen@norgren.ca}}
\def\phone{\href{tel:2369899969}{(236)~989~9969}}

\begin{document}
\header{\firstname{}}{\lastname{}}
       {\jobtitle{}}


% In the aside, each new line forces a line break
\begin{aside}
  \section{Contact}
    \address{}
    ~
    \email{}
    \phone{}
  \section{Programming}
    C, C++, C Varianta,
    Python, Puppet,
    Bash, Fish
  \section{Skills}
    Network Security
    Troubleshooting
    System Administration
    Data Recovery/Backup
    Revision Control
    Shell Scripting
    Continuous Delivery
    Technical Writing
  \section{Languages}
    English \& French
\end{aside}

\section{Objective}

To contune 

\section{About}

I am a holistic technologist -- I focus on viewing complex computer systems as a single entity. I am able to craft ingenious solutions using limited resources -- solving problems that were formerly considered impossible.

\section{Experience}

\begin{entrylist}
  \entry
    {2012 - 2015}
    {\href{https://www.linkedin.com/company-beta/3491430}{Poetica Ltd.} - DevOps Engineer}
    {London, UK}
    {Design and implementation of scalable EC2 cloud provisioning and automation system for development. Managed migration to Softlayer for launch of public beta. Company has since been purchased by Condé Nast.}
  \entry
    {2011}
    {Superior Seating Hospitality - Migration Specialist}
    {Toronto, Ontario}
    {Migrated from a poorly managed and fragmented IT/support department to a more cost effective and stable solution.}
  \entry
    {1996 - 2010}
    {\href{https://www.marketvolume.com}{Highlight Investments Inc.} - Co-Founder}
    {North Vancouver, BC}
    {Architect for the company's IT infrastructure as well as creation of a new form of stock market analysis. Database and network infrastructure responsible for collecting and archiving tens of thousands of stocks and derivatives data in real-time.}
\end{entrylist}

\section{Education}

\begin{entrylist}
  \entry
    {2010–2013}
    {B.Tech - Bachelor of Technology}
    {BCIT}
    {Network Security \& Administration}
  \entry
    {2007–2010}
    {Diploma - Computer Systems \& Technology}
    {BCIT}
    {Data Communications and Inter-networking}
\end{entrylist}

\section{Publications}

\begin{entrylist}
  \entry
    {2005}
    {Patent}
    {\href{https://www.google.com/patents/US7813984?dq=7813984&ei=Ce52UvW8PIKsjAKgioDoBw}{US7813984 B2}}
    {System for determining modulated volume for a tradeable financial element.}
  \entry
    {May 2004}
    {Volume Spikes \& Index Reversals}
    {\href{https://www.scribd.com/document/181246479/Volume-Spikes-Index-Reversals-The-Technical-Analyst-May-2004}{The Technical Analyst}}
    {}
  \entry
    {June 2004}
    {Website for Traders}
    {\href{https://www.scribd.com/doc/181244683/Website-for-Traders-Stocks-Commodities-June-2004}{Stocks \& Commodities}}
    {}
\end{entrylist}

\end{document}